Hierarchical storage management in user space for neuroimaging applications

### 2024-08-02 paper/sea-neuro/paper-neuro.tex
Add missing subsections to neuro paper

	Neuroimaging open-data initiatives have led to increased availability of large
  scientific datasets. While these datasets are shifting the processing
  bottleneck from compute-intensive to data-intensive, current standardized
  analysis tools have yet to adopt strategies that mitigate the costs
  associated with large data transfers. A major challenge in adapting neuroimaging
  applications for data-intensive processing is that they must be entirely
  rewritten. To facilitate data management for standardized neuroimaging tools, we
  developed Sea, a library that intercepts and redirects application read and
  write calls to minimize data transfer time. In this paper, we investigate the
  performance of Sea on three preprocessing pipelines implemented using standard toolboxes (FSL,
  SPM and AFNI), using three neuroimaging datasets of different sizes
  (OpenNeuro's ds001545, PREVENT-AD and the HCP dataset) on two high-performance
  computing clusters. Our results demonstrate that Sea provides large speedups (up to 32$\times$) when
  the shared file system's (e.g. Lustre) performance is deteriorated. When the
  shared file system is not overburdened by other users, performance is
  unaffected by Sea, suggesting that Sea's overhead is minimal even in cases
  where its benefits are limited. Overall, Sea is beneficial, even when performance gain
  is minimal, as it can be used to limit the number of files created on parallel file systems.
\end{abstract}
\begin{document}

@@

@@

    %Busy writers
    \section{Conclusion and Future work}

@@

>>>>

  Neuroimaging open-data initiatives have led to increased availability of large
  scientific datasets. While these datasets are shifting the processing bottleneck
  from compute-intensive to data-intensive, current standardized analysis tools
  have yet to adopt strategies that mitigate the costs associated with large data
  transfers. A major challenge in adapting neuroimaging applications for data-intensive
  processing is that they must be entirely rewritten. To facilitate data management for
  standardized neuroimaging tools, we developed Sea, a library that intercepts and
  redirects application read and write calls to minimize data transfer time. In this
  paper, we investigate the performance of Sea on three preprocessing pipelines applied
  to three different neuroimaging datasets on two high-performance computing clusters.
  Our results demonstrate that Sea provides large speedups (up to 32$\times$) when the
  shared file system’s performance is deteriorated. When the shared file system is not
  overburdened by other users, performance is unaffected by Sea, suggesting that Sea’s
  overhead is minimal even in cases where its benefits are limited.

	% Neuroimaging open-data initiatives have led to increased availability of large
  % scientific datasets. While these datasets are shifting the processing
  % bottleneck from compute-intensive to data-intensive, current standardized
  % analysis tools have yet to adopt strategies that mitigate the costs
  % associated with large data transfers. A major challenge in adapting neuroimaging
  % applications for data-intensive processing is that they must be entirely
  % rewritten. To facilitate data management for standardized neuroimaging tools, we
  % developed Sea, a library that intercepts and redirects application read and
  % write calls to minimize data transfer time. In this paper, we investigate the
  % performance of Sea on three preprocessing pipelines implemented using standard toolboxes (FSL,
  % SPM and AFNI), using three neuroimaging datasets of different sizes
  % (OpenNeuro's ds001545, PREVENT-AD and the HCP dataset) on two high-performance
  % computing clusters. Our results demonstrate that Sea provides large speedups (up to 32$\times$) when
  % the shared file system's (e.g. Lustre) performance is deteriorated. When the
  % shared file system is not overburdened by other users, performance is
  % unaffected by Sea, suggesting that Sea's overhead is minimal even in cases
  % where its benefits are limited. Overall, Sea is beneficial, even when performance gain
  % is minimal, as it can be used to limit the number of files created on parallel file systems.
\end{abstract}
\begin{document}

@@

    \subsection{Conclusion and Future work}

@@

    %Busy writers

@@

    \section{Acknowledgements}
    Val\'erie Hayot-Sasson was funded by the Canadian Open
    Neuroscience Platform (CONP) Scholar Award. This work
    was also supported by the Canada Foundation for Innova-
    tion as well as the Canada Research Chairs program.

    \section{Author Contributions}
    VHS contributed to idea development, experimental and model design, implementation of experiments and
    evaluation. TG contributed to idea development, experimental design and implementation.

    \section{Competing Interests}
    The authors declare no competing interests.
